---
title: "graphic_description"
description: |
  Graphic analysis of sea urchins.
author:
  - name: Leheureux Lara
    url: {}
date: 11-18-2020
output:
  distill::distill_article:
    self_contained: false
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

```{r}
SciViews::R
```

```{r}
urchin <- data.io::read("urchin_bio", package = "data.io")
```

The subject represented here is realized with a data set on "urchin_bio" grouping several specific variables. Through R-studio, I created a graph that analyses the possible link, taking into account the origins, between the weight of the solid parts of urchin and the weight of lantern (the jaw).

```{r}
chart(data = urchin_bio, solid_parts ~ lantern %fill=% origin) +
  geom_violin(na.rm = TRUE)
```

 If we look at the data that are analyzed, we can see that, generally, the weight of the solid part is condensed between 0 and 20-30 g and decreases afterwards while the weight of the lantern is quite variable. It can also be seen that individuals with an average lantern weight between 0.4 and 1.0 have a greater weight of solid part. For origins, it may be noted that urchins of Farm origin have more variable data than Fishery but are globally the same.
